---
title: "HLL Textbook Replication Project"
subtitle: 'Assessing introspective linguistic judgments quantitatively: The case of The Syntax of Chinese'
author: "Zhong Chen, Yuhang Xu, Zhiguo Xie"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    highlight: tango
    toc: yes
    toc_depth: 3
    toc_float: true
   # number_sections: true
---

```{r setup, include=FALSE,cache=TRUE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(lmerTest)
library(scales)
library(emmeans)
```

# Acceptability Judgment Experiment
## Cleaning data: AJ Experiment
```{r message=FALSE, warning=FALSE}
###set your working directory to the source file localtion###

d.HLL<-read.csv("../data/HLL-TEST-2018_08.44_numeric_values.csv")
header <- names(d.HLL)  
d.HLL<- read.csv("../data/HLL-TEST-2018_08.44_numeric_values.csv", col.names = header, skip = 2) 
item.code.keys <- read.csv("../data/itemcodekeyHLL.csv")#add conditions

todrop <- c("StartDate","EndDate","Finished","RecordedDate","RecipientLastName","RecipientFirstName", "RecipientEmail","ExternalReference" ,"LocationLatitude","LocationLongitude" ,"DistributionChannel", "IPAddress","UserLanguage")

d.HLL%>% 
  select(-one_of(todrop)) %>%
  rename(ExpLists = FL_4_DO, SubGender = Q1.6, SubAge =Q1.7, L1= Q1.8 , Education=Q1.9,Dialects= Q1.15_1, SubID=ResponseId , L2=Q1.16_1 )%>%
  filter(Status == 0 & Progress==100 ) %>%  #real participants+finished 
  select(-Status,-Progress,-Q1.3,-Q1.4,- Q1.17,-starts_with("Q2."),-starts_with("Q8.")) %>%
  gather(key = Qnumber,value=choice,Q3.1:Q7.161,na.rm = T) %>%#widd to long
  arrange(SubID, Qnumber) %>% 
  group_by(SubID) %>%   #add scores
  mutate(zscore = scale(choice)) %>% 
  ungroup()%>%
  mutate_at(vars(matches("_DO")), as.character)%>%
  mutate_at(vars(matches("ExpLists")), as.character)%>%
  mutate(TrialOrder = case_when(ExpLists == "list-pair-1" ~ list.pair.1_DO,
                                ExpLists == "list-pair-2" ~ list.pair.2_DO,
                                ExpLists == "list-filler-a" ~ list.filler.a_DO,
                                ExpLists == "list-filler-b" ~ list.filler.b_DO,
                                ExpLists == "list-filler-c" ~ list.filler.c_DO))%>%
  select(-matches("_DO"))%>%
  inner_join(y=item.code.keys)->d.HLL.cond #add experimental conditions

#add trial order sequence 
seqnum=as.character(c(1:158))
d.HLL.cond %>%
  select(SubID,TrialOrder) %>%
  distinct()%>%
  separate(TrialOrder, into=seqnum, sep = "\\|")%>%
  gather(key = QSEQ,value=Qnumber,"1":"158",na.rm = T) %>%#widd to long
  inner_join(y=d.HLL.cond)->d.HLL.cond
```

## Participants & Lists information: AJ Experiment  
```{r}
#subjects# in each group
  d.HLL.cond %>%
  group_by(ExpLists) %>%
  summarise(count = n_distinct(SubID))

#subjects age infor
d.HLL.cond %>%
  group_by(SubGender) %>%
  summarise(count = n_distinct(SubID),age_mean = mean(as.numeric(as.character(SubAge))),age_SD = sd(as.numeric(as.character(SubAge))))

#subjects who have "linguistics" related background
d.HLL.cond %>%
  filter(grepl("语言",Q1.12)==T|grepl("语言",Q1.13)==T) %>%
  summarise(count = n_distinct(SubID))
```


```{r}
#check "catch" trials
#exclude subjects failed any catch-question
d.HLL.cond  %>%
  filter(Category=="catch") %>%
  select(SubID,choice,SenType,ExpLists)  %>%
  mutate(CorrectA = ifelse(SenType == "catch2", 2, 5)) %>%
  filter(choice!=CorrectA) %>%
  select(SubID)%>%
  unique()%>%
  droplevels()%>%
  .$SubID->sub.exclude
  
#subjects exclude in each group
d.HLL.cond  %>%
  filter(Category=="catch") %>%
  select(SubID,choice,SenType,ExpLists)  %>%
  mutate(CorrectA = ifelse(SenType == "catch2", 2, 5)) %>%
  filter(choice!=CorrectA) %>%
  group_by(ExpLists) %>%
  summarise(count = n_distinct(SubID))
```



## All data: "pair" + "other" lists
```{r}
d.HLL.cond %>%
  filter(!SubID%in%sub.exclude) %>%
  filter(Category!="catch") %>%
  mutate(SenCon=ifelse(SenType=="g","good",
                       ifelse(SenType=="q","questionable","bad")))->d.HLL.all

d.HLL.all %>%
  group_by(SenCon) %>%
  summarise(MeanScore=mean(choice))
```

```{r}
#theme for plots
theme.yuhang <- theme_bw()+
  theme(axis.text=element_text(size=12),axis.title=element_text(size=14,face="bold"))+
  theme(legend.text = element_text(size=12))+
  theme(legend.title = element_text(size=14, face="bold"))+
  theme(legend.title.align  = 0.5)+
  theme(strip.text = element_text(size=12))+
  theme(title = element_text(size=14, face="bold"))+
  theme(plot.title = element_text(hjust = 0.5))
theme_set(theme.yuhang)
```

```{r warning=FALSE}
ggplot(d.HLL.all, aes(x = SenCon, y=as.numeric(choice)))+
  stat_summary(geom = "bar",fun.y = "mean", aes(fill=SenCon),colour="black")+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",width = 0.1)+
  scale_x_discrete(limits=c("bad","questionable","good"))+
  scale_fill_manual(limits=c("bad","questionable","good"),values=c("#F8766D", "#00BA38", "#00BFC4"))+
  coord_cartesian(ylim =c(0,7))+
  scale_y_continuous(breaks=seq(0,7,1))+
  labs(x = "Sentence Type", y="Acceptability Rating")+
  guides(colour=FALSE,fill=FALSE)->p.overall.ex1
p.overall.ex1
```

```{r message=FALSE, warning=FALSE}
d.HLL.all %>%
  mutate(contrast_BvQ =ifelse(SenCon == "bad",1,0))%>%
  mutate(contrast_GvQ =ifelse(SenCon == "good",1,0))->d.HLL.all

#use question as the baseline level
m.alldata<-lmer(zscore~contrast_BvQ+contrast_GvQ+(1+contrast_BvQ+contrast_GvQ |SubID)+(1+contrast_BvQ+contrast_GvQ|ItemNum),data=d.HLL.all)
summary(m.alldata)$coefficients

# m.alldata.raw<-lmer(choice~contrast_BvQ+contrast_GvQ+(1+contrast_BvQ+contrast_GvQ|SubID)+(1+contrast_BvQ+contrast_GvQ|ItemNum),data=d.HLL.all)
# summary(m.alldata.raw)$coefficients


# use bad as the baseline level
#summary(lmer(choice~SenCon+(1+SenCon|SubID)+(1+SenCon|ItemNum),data=d.HLL.all))
# m.allbadasbaseline<-lmer(choice~SenCon+(1+SenCon|SubID)+(1+SenCon|ItemNum),data=d.HLL.all)
# summary(m.allbadasbaseline)

m.allbadasbaseline.z<-lmer(zscore~SenCon+(1+SenCon|SubID)+(1+SenCon|ItemNum),data=d.HLL.all)
summary(m.allbadasbaseline.z)$coefficients
```

```{r}
#we will look at "other" lists  only!
# I also tried all data
d.HLL.all %>%
  filter(Category!="pair")%>%
  group_by(ItemNum, SenCon)  %>%
  summarise(Avescore=mean(choice)) %>%
  ggplot(aes(x = ItemNum, y=Avescore,label=ItemNum))+
  geom_text(aes(colour=SenCon))+
  labs(x = "Contrast Number", y="Average Acceptability Rating")+
  scale_color_manual(name="Sentence Type",limits=c("bad","questionable","good"),values=c("#F8766D", "#00BA38", "#00BFC4"))+
  geom_hline(yintercept = 4,colour="grey",linetype = 2,size = 0.3)+
  theme_bw()+
  theme(axis.text.x = element_blank(),axis.ticks.x = element_blank(),line = element_blank())
```


## Visualiztions: AJ Experiment - "pair" lists 
```{r}
#we will look at the "pair" first
d.HLL.cond %>%
  filter(!SubID%in%sub.exclude) %>%
  filter(Category!="catch") %>%
  mutate(SenCon=ifelse(SenType=="g","good",
                       ifelse(SenType=="q","questionable","bad"))) %>%
  filter(ExpLists %in% c("list-pair-1","list-pair-2")) -> d.HLL.pair  
```



```{r raw score plot, message=FALSE, warning=FALSE}
#plot for all pairs
ggplot(d.HLL.pair, aes(x = SenCon, y=as.numeric(choice)))+
  geom_jitter(alpha = 0.1, aes(colour=SenCon))+
  stat_summary(geom = "line", fun.y = "mean", aes(group=ItemNum),alpha=0.2) +
  stat_summary(geom = "point",fun.y = "mean", aes(colour=SenCon),size = 6)+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",width = 0.1)+
  scale_y_continuous(breaks=seq(0,7,1))+
  labs(x = "Sentence Type", y="Acceptability Rating")+
  geom_hline(yintercept = 4,colour="blue",linetype = 2)+
  guides(colour=FALSE,fill=F)->p.pair.all
p.pair.all

#by-item plot
ggplot(d.HLL.pair,aes(x = SenCon, y=as.numeric(choice)))+
  stat_summary(geom = "point",fun.y = "mean", aes(color=SenCon))+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",width = 0.1)+
  geom_hline(yintercept = 4,colour="blue",linetype = 2)+
  facet_wrap(~ItemNum)+
  scale_y_continuous(breaks=seq(-1,8,2))+
  labs(x = "Sentence Type", y="Acceptability Rating")+
  guides(colour=FALSE) +
  theme_bw()->p.pair.byitem
#p.pair.byitem see plots folder for item-by-item plot
```

```{r z-score plot, message=FALSE, warning=FALSE}
#Z-score version plot for all pairs
ggplot(d.HLL.pair, aes(x = SenCon, y=as.numeric(zscore)))+
  geom_jitter(alpha = 0.05, aes(colour=SenCon))+
  stat_summary(geom = "line", fun.y = "mean", aes(group=ItemNum),alpha=0.2) +
  stat_summary(geom = "point",fun.y = "mean", aes(color=SenCon),size=6)+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",width = 0.1)+
  labs(x = "Sentence Type", y="Acceptability Rating")+
  geom_hline(yintercept = 0,colour="blue",linetype = 2)+
  guides(colour=FALSE)->p.pair.all.z
p.pair.all.z

#z-score by-item plot
ggplot(d.HLL.pair,aes(x = SenCon, y=as.numeric(zscore)))+
 # geom_violin(alpha = 0.5,aes(colour=SenCon))+
  stat_summary(geom = "point",fun.y = "mean", aes(color=SenCon),size=2)+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",width = 0.1)+
  geom_hline(yintercept = 0,colour="blue",linetype = 2)+
  facet_wrap(~ItemNum)+
  scale_y_continuous(breaks=seq(-3,3,1))+
  labs(x = "Sentence Type", y="Acceptability Rating")+
  guides(colour=FALSE) +
  theme_bw()->p.pair.byitem.z
#p.pair.byitem.z See plots folder for item-by-item plot
```

```{r difference score}
# difference scores between good and bad 
d.HLL.pair %>%
  group_by(ItemNum, SenCon)  %>%
  summarise(Avescore=mean(choice)) %>%
  mutate(DiffScore =  Avescore-lag(Avescore)) %>%
  filter(!is.na(DiffScore))  %>%
  ggplot(aes(x = ItemNum, y=DiffScore,label = ItemNum))+
  geom_text(size=3)+
  labs(x = "Contrast Number", y="Acceptability Rating Difference")+
  geom_hline(yintercept = 0,colour="blue",linetype = 2)+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        line = element_blank())->p.pair.differscore
p.pair.differscore
```

```{r sequence data plot, message=FALSE, warning=FALSE}
ggplot(d.HLL.pair,aes(x =  as.numeric(QSEQ) , y=as.numeric(choice),colour=SenCon))+
  stat_summary(geom = "point",fun.y = "mean")+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",aes(colour=SenCon),width = 0.1,alpha=0.5)+
  geom_smooth(method = "lm")+
  geom_hline(yintercept = 4,colour="blue",linetype = 2)+
  labs(x = "Trial Sequence", y="Mean Acceptability Rating")+
  guides(colour=guide_legend(title="Sentence Type")) ->p.pair.sequence

p.pair.sequence
```

## Analysis: AJ Experiment 
```{r}
#coding variables
d.HLL.pair$SenTypeC<-ifelse(d.HLL.pair$SenCon=="good", 1,-1)
d.HLL.pair$QSEQ<-as.numeric(d.HLL.pair$QSEQ)
d.HLL.pair$SubAge<-as.numeric(d.HLL.pair$SubAge)

#check control variables
m.control<-lmer(choice~QSEQ+SubGender+SubAge+Education+(1|SubID)+(1|ItemNum),data=d.HLL.pair )
summary(m.control)$coefficients

m.control.z<-lmer(zscore~QSEQ+SubGender+SubAge+Education+(1|SubID)+(1|ItemNum),data=d.HLL.pair )
summary(m.control.z)$coefficients
```


```{r}
#all pairs raw score models
m.all<-lmer(choice~SenTypeC+(1+SenTypeC|SubID)+(1+SenTypeC|ItemNum),data=d.HLL.pair)
summary(m.all)$coefficients

#all pairs z score models
m.all.z<-lmer(zscore~SenTypeC+(1+SenTypeC|SubID)+(1+SenTypeC|ItemNum),data=d.HLL.pair)
summary(m.all.z)$coefficients
```

```{r}
#item by item analysis
itemlist<-unique(d.HLL.pair$ItemNum)

#run models for each item and print t values for non-sig items
nonsigitem <- c()
for (i in itemlist){
  m.a<-summary(lm(choice~SenTypeC,data=subset(d.HLL.pair, ItemNum==i)))$coef[, "t value"]
  if (getElement(m.a, "SenTypeC") < 2){print(paste(i,"  ",formatC(getElement(m.a, "SenTypeC"),digits=2,format="f")))
    nonsigitem[i]<-i}
}
print(paste0(length(unname(nonsigitem)), " non-sig/reversed in raw data"))
```

```{r}
#how about z-scores?
nonsigitem.z <- c()
for (i in itemlist){
  m.z<-summary(lm(zscore~SenTypeC,data=subset(d.HLL.pair, ItemNum==i)))$coef[, "t value"]
  if (getElement(m.z, "SenTypeC") < 2){print(paste(i,"  ",formatC(getElement(m.z, "SenTypeC"),digits=2,format="f")))
    nonsigitem.z[i]<-i}
}
print(paste0(length(unname(nonsigitem.z)), " non-sig/reversed in z-transformed data"))
```

```{r}
nonsig<-unname(nonsigitem)
nonsig.z<-unname(nonsigitem.z)

print("non-sig/reversed in both raw and z-transformed data")
intersect(nonsig,nonsig.z)
print("non-sig/reversed in raw data only")
(onlyraw<-setdiff(nonsig,nonsig.z))

bothnonsig<-intersect(nonsig,nonsig.z)
```

```{r message=FALSE, warning=FALSE}
nonsig<-unname(nonsigitem)
#by-item plot for nonsig
ggplot(subset(d.HLL.pair,ItemNum %in% nonsig ),aes(x = SenCon, y=as.numeric(choice)))+
  geom_jitter(alpha = 0.15, aes(colour=SenCon))+
  stat_summary(geom = "point",fun.y = "mean", aes(color=SenCon),size=2)+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",colour="black",width = 0.2)+
  geom_hline(yintercept = 4,colour="blue",linetype = 2)+
  geom_rect(data = subset(d.HLL.pair,ItemNum %in%bothnonsig),
            xmin = -Inf,xmax = Inf,ymin = -Inf,ymax = Inf,
            colour="red",size=1.5,alpha = 0) +
  facet_wrap(~ItemNum)+
  scale_y_continuous(breaks=seq(-1,7,2))+
  labs(x = "Sentence Type", y="Acceptability Rating",title="Non-significant/reversed contrasts")+
  guides(colour=FALSE) +
  theme_bw()->p.nonsig.byitem
p.nonsig.byitem

#show items that non-sig in both rawdata and z-data
ggplot(subset(d.HLL.pair,ItemNum %in% nonsig.z),aes(x = SenCon, y=as.numeric(choice)))+
  geom_jitter(alpha = 0.15, aes(colour=SenCon))+
  stat_summary(geom = "point",fun.y = "mean", aes(color=SenCon),size=1.5)+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",colour="black",width = 0.25)+
  geom_hline(yintercept = 4,colour="blue",linetype = 2)+
  facet_wrap(~ItemNum)+
  scale_y_continuous(breaks=seq(-1,7,2))+
  labs(x = "Sentence Type", y="Acceptability Rating")+
  guides(colour=FALSE)->p.nonsig.inboth.byitem
p.nonsig.inboth.byitem

#show items that non-sig in only raw data
ggplot(subset(d.HLL.pair,ItemNum %in% onlyraw),aes(x = SenCon, y=as.numeric(choice)))+
  geom_jitter(alpha = 0.15, aes(colour=SenCon))+
  stat_summary(geom = "point",fun.y = "mean", aes(color=SenCon),size=1.5)+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",colour="black",width = 0.25)+
  geom_hline(yintercept = 4,colour="blue",linetype = 2)+
  facet_wrap(~ItemNum)+
  scale_y_continuous(breaks=seq(-1,7,2))+
  labs(x = "Sentence Type", y="Acceptability Rating")+
  guides(colour=FALSE)->p.nonsig.onlyraw.byitem
#p.nonsig.onlyraw.byitem
```

```{r message=FALSE, warning=FALSE}
#by-item plot for nonsig~zcores&raw
ggplot(subset(d.HLL.pair,ItemNum %in% nonsig.z ),aes(x = SenCon, y=as.numeric(zscore)))+
  geom_jitter(alpha = 0.2, aes(colour=SenCon))+
  stat_summary(geom = "point",fun.y = "mean", aes(color=SenCon),size=2)+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",aes(colour=SenCon),width = 0.2)+
  geom_hline(yintercept = 0,colour="blue",linetype = 2)+
  facet_wrap(~ItemNum)+
  labs(x = "Sentence Type", y="Acceptability rating (z-transformed)",title="Non-significant/reversed contrasts")+
  guides(colour=FALSE) +
  theme_bw()->p.nonsig.byitem.z
p.nonsig.byitem.z
```

## Non significant items: AJ Experiment
See "Appendix" of the paper for details  
```{r}
#getting the test items
unname(nonsigitem)
```

## Items for the Forced-choice Experiment
### Control 1 item
```{r message=FALSE}
# getting the control pairs
itemlist<-unique(d.HLL.pair$ItemNum)
itemtvalue <- c()
itemname <- c()
x<-1
for (i in itemlist){
  m.a<-summary(lm(choice~SenTypeC,data=subset(d.HLL.pair, ItemNum==i)))$coef[, "t value"]
  itemtvalue[x]<-getElement(m.a, "SenTypeC")
  itemname[x]<-i
  x<-x+1
}

d.itemt <- data.frame(itemnames=itemname,tvalue=itemtvalue)
d.itemt %>%
  arrange(-tvalue) %>%
  top_n(29) %>%   ## used c5-69 and c8-71c as expt instruction examples
  select(itemnames)%>%
  unique() %>% 
  .$itemnames->controlgroup
remove <- c ("c5-69", "c8-71c")
 controlgroup.p<-controlgroup[! controlgroup %in% remove]
```

```{r message=FALSE, warning=FALSE}
ggplot(subset(d.HLL.pair,ItemNum %in% controlgroup.p ),aes(x = SenCon, y=as.numeric(choice)))+
  geom_jitter(alpha = 0.05, aes(colour=SenCon))+
  stat_summary(geom = "point",fun.y = "mean", aes(color=SenCon),size=2)+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",colour="black",width = 0.2)+
  geom_hline(yintercept = 4,colour="blue",linetype = 2)+
  facet_wrap(~ItemNum)+
  scale_y_continuous(breaks=seq(-1,7,2))+
  labs(x = "Sentence Type", y="Acceptability Rating",title="Forced choice control 1")+
  guides(colour=FALSE) +
  theme_bw()->p.control.byitem

p.control.byitem
```

# Forced Choice Experiment
## Cleaning data: FC Experiment
```{r}
d.fc<-read.csv("../data/HLL-ForcedChoice-20180922.csv")
d.fc<-tail(d.fc,-2)
item.code.FC<-read.csv("../data/item.code.FC.csv")
```

```{r}
#now we check catch trials 
d.fc%>% 
  filter(Status == 0 & Progress==100 ) %>%  #non-testing+finished
  select(ResponseId,starts_with("Q3.55"),starts_with("Q3.56"))%>%
  mutate(Correct55 = ifelse(Q3.55_DO == "2|1", 2, 1)) %>%
  mutate(Correct56 = ifelse(Q3.56_DO == "2|1", 1, 2))  %>%
 # filter(Q3.55!=Correct55 & Q3.56!=Correct56)%>%  ## failed both catch q 7 subjects
  filter(Q3.55!=Correct55 | Q3.56!=Correct56)%>% ## failed any catch q (22 subjects)
  select(ResponseId)%>%
  unique()%>%
  droplevels()%>%
  .$ResponseId->subtoexclude
print(paste0(n_distinct(subtoexclude), " subjects excluded"))
```

```{r message=FALSE, warning=FALSE}
d.fc%>% 
  select(-one_of(todrop))%>% 
  rename(SubGender = Q1.6, SubAge =Q1.7, L1= Q1.8 , 
         Education=Q1.9,Dialects= Q1.15_1, SubID=ResponseId , 
         L2=Q1.16_1,ExpOrder=Experiment_DO)%>%
  filter(Status == 0 & Progress==100 ) %>%  #non-testing+finished
  select(-Status,-Progress,-Q1.3,-Q1.4,- Q1.17,-starts_with("Q2."),-starts_with("Q4."),-FL_4_DO) %>%
  filter(!SubID%in%subtoexclude) %>%
  select(-ends_with("_DO"),-Q3.55,-Q3.56)%>%
  gather(key = Qnumber,value=choice,Q3.1:Q3.54)%>%
  inner_join(y=item.code.FC)%>%
  mutate(GroupNew=ifelse(Group=="test"&ItemNum%in%nonsig.z,"test",ifelse(Group=="control"&!ItemNum%in%nonsigitem,"control 1", "control 2")))->d.fc.ready#3 groups now control 1 control2() and test 
```

## Participants & Lists information: AJ Experiment  
```{r}
#Participants# mean age
d.fc.ready%>%
  group_by(SubGender) %>%
  summarise(count = n_distinct(SubID),age_mean = mean(as.numeric(as.character(SubAge))),age_SD = sd(as.numeric(as.character(SubAge))))

#Participants who have linguistics related background
d.fc.ready %>%
  filter(grepl("语言",Q1.12)==T|grepl("语言",Q1.13)==T) %>%
  summarise(count = n_distinct(SubID))
```

## Visualiztions: FC Experiment 
```{r warning=F}
#visualiztion: general pattern 
d.fc.ready %>%
  mutate(answer=ifelse(choice==GoodChoice,"Good","Bad"))%>%
  group_by(GroupNew,ItemNum,answer) %>%
  tally()%>%
  mutate(Proportion = n / sum(n),se = sqrt(Proportion*(1-Proportion)/n))%>%
  ggplot(aes(x=GroupNew,y=Proportion,fill=answer))+
  stat_summary(geom = "bar", fun.y = "mean", aes(fill=answer),color="black",position = position_dodge())+
  stat_summary(geom = "errorbar", fun.data = "mean_cl_boot",position = position_dodge(width = 0.9),width=0.3)+
  scale_y_continuous(labels=percent_format())+
  labs(y="Proportion of Choice",x="Group")->p.overall.ex2
p.overall.ex2
```

```{r warning=FALSE}
#Control group 1: Individual-item
d.fc.ready %>%
  mutate(answer=ifelse(choice==GoodChoice,"Good","Bad"))%>%
  group_by(Group,ItemNum,answer) %>%
  tally()%>%
  mutate(Proportion = n / sum(n),se = sqrt(Proportion*(1-Proportion)/n))%>%
  filter(Group=="control")%>%
  ggplot(aes(x=answer,y=Proportion,fill=answer))+
  stat_summary(geom = "bar", fun.y = "mean", aes(fill=answer),color="black",position = position_dodge())+
  scale_y_continuous(labels=percent_format())+
  facet_wrap(~ItemNum,ncol = 7)+
  labs(y="Proportion of Choice",title="Control group 1: Individual-item")+
  scale_fill_discrete(name="Answer")+
  theme_bw(base_size = 9)+
  theme(legend.position = c(0.95, 0.09))
```

```{r warning=FALSE}
d.fc.ready %>%
  mutate(answer=ifelse(choice==GoodChoice,"Good","Bad"))%>%
  group_by(GroupNew,ItemNum,answer) %>%
  tally()%>%
  mutate(Proportion = n / sum(n),se = sqrt(Proportion*(1-Proportion)/n))%>%
  filter(GroupNew=="test")->d.fc.testgroup

ggplot(data=d.fc.testgroup,aes(x=answer,y=Proportion))+
  stat_summary(geom = "bar", fun.y = "mean", aes(fill=answer),color="black",position = position_dodge())+
  geom_hline(yintercept = 0.5,colour="blue",linetype = 2)+
  scale_y_continuous(labels=percent_format())+
  facet_wrap(~ItemNum,ncol = 6)+
  labs(y="Proportion of Choice",title="Test group: Individual-item")+
  scale_fill_discrete(name="Answer")+
  theme_bw(base_size = 9)+
  theme(legend.position = c(0.95, 0.09))

```

## Analysis: FC Experiment
```{r message=FALSE, warning=FALSE}
#Comparing the "good" vs. "bad" choices. Does the "good"  sigifictly higher than the "bad"(or 50%)?
#overall: all items 
#control group
d.fc.ready %>%
  group_by(SubID,GroupNew) %>%
  tally() %>%
  inner_join(d.fc.ready)%>%
  mutate(answerC=ifelse(choice==GoodChoice,1,0))  %>%
  mutate(emplogit=log((answerC+0.5)/(n-answerC+0.5)))->d.fc.ready.model

```

```{r}
#Three groups: control 1 2 and test
summary(glmer(answerC~1+(1|SubID)+(1|ItemNum),subset(d.fc.ready.model,GroupNew=="control 1"),family = binomial(link = "logit")))$coefficient
summary(glmer(answerC~1+(1|SubID)+(1|ItemNum),subset(d.fc.ready.model,GroupNew=="control 2"),family = binomial(link = "logit")))$coefficient
summary(glmer(answerC~1+(1|SubID)+(1|ItemNum),subset(d.fc.ready.model,GroupNew=="test"),family = binomial(link = "logit")))$coefficient
```

```{r}
#item-by-item 
#control group 1
itemlist.fc<-unique(subset(d.fc.ready.model,GroupNew=="control 1")$ItemNum)

#run models for each item and print z values 
#controllist.fc <- c()
for (i in itemlist.fc){
  m.fc<-summary(glm(answerC~1,data=subset(d.fc.ready.model,ItemNum==i),family = binomial(link = "logit")))$coef[, "z value"]
  print(paste(i,"  ",formatC(m.fc,digits=2,format="f")))
}
```

```{r}
#item-by-item 
#control group 2
itemlist.fc<-unique(subset(d.fc.ready.model,GroupNew=="control 2")$ItemNum)

#run models for each item and print z values 
#controllist.fc <- c()
for (i in itemlist.fc){
  m.fc<-summary(glm(answerC~1,data=subset(d.fc.ready.model,ItemNum==i),family = binomial(link = "logit")))$coef[, "z value"]
  print(paste(i,"  ",formatC(m.fc,digits=2,format="f")))
}



#get non significent or reversed pairs 
nonsigitem.fc.c2 <- c()
for (i in itemlist.fc){
  m.fc<-summary(glm(answerC~1,data=subset(d.fc.ready.model,ItemNum==i),family = binomial(link = "logit")))$coef[, "z value"]
  if (m.fc < 2){
    print(paste(i,"  ",formatC(m.fc,digits=2,format="f")))
    nonsigitem.fc.c2[i]<-i}
}
```

```{r}
#compare the choice of the good sentences in control and  test group
contrasts(d.fc.ready.model$Group)<-  contr.sum(2)
#control    1  test      -1

m.controlvstest<-glmer(answerC~Group+(1+Group|SubID)+(1+Group|ItemNum),data=d.fc.ready.model,
                       family = binomial(link = "logit"),
                       control=glmerControl(optimizer="bobyqa"))

summary(m.controlvstest)$coefficients
#People chose more good sentences (or less bad sentences ) for the control group than the test group. 
```


```{r}
#item-by-item 
#test group
itemlist.fc<-unique(subset(d.fc.ready.model,GroupNew=="test")$ItemNum)

#run models for each item and print z values 
#controllist.fc <- c()
for (i in itemlist.fc){
  m.fc<-summary(glm(answerC~1,data=subset(d.fc.ready.model,ItemNum==i),family = binomial(link = "logit")))$coef[, "z value"]
  print(paste(i,"  ",formatC(m.fc,digits=2,format="f")))
}
```

```{r}
#get non significent or reversed pairs 
nonsigitem.fc <- c()
for (i in itemlist.fc){
  m.fc<-summary(glm(answerC~1,data=subset(d.fc.ready.model,ItemNum==i),family = binomial(link = "logit")))$coef[, "z value"]
  if (m.fc < 2){
    print(paste(i,"  ",formatC(m.fc,digits=2,format="f")))
    nonsigitem.fc[i]<-i}
}
```

```{r warning=FALSE}
#add  highlight n.s. contrasts to 
nonsigitemfc<-unname(nonsigitem.fc)

d.fc.ready %>%
  mutate(answer=ifelse(choice==GoodChoice,"Good","Bad"))%>%
  group_by(GroupNew,ItemNum,answer) %>%
  tally()%>%
  mutate(Proportion = n / sum(n),se = sqrt(Proportion*(1-Proportion)/n))%>%
  filter(GroupNew=="test")->d.fc.testgroup

ggplot(data=d.fc.testgroup,aes(x=answer,y=Proportion))+
  stat_summary(geom = "bar", fun.y = "mean", aes(fill=answer),color="black",position = position_dodge())+
  geom_hline(yintercept = 0.5,colour="blue",linetype = 2)+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  facet_wrap(~ItemNum,ncol = 6)+
  geom_rect(data = subset(d.fc.testgroup,ItemNum %in% nonsigitemfc),
            xmin = -Inf,xmax = Inf,ymin = -Inf,ymax = Inf,
            colour="red",size=1.5,alpha = 0)+
  labs(y="Proportion of Choice",title="Test group: Individual-item")+
  scale_fill_discrete(name="Answer")+
  theme_bw(base_size = 12)+
  theme(legend.position = c(0.95, 0.09))->p.fc.test.hl
p.fc.test.hl
```

```{r warning=FALSE}
d.fc.ready %>%
  mutate(answer=ifelse(choice==GoodChoice,"Good","Bad"))%>%
  group_by(GroupNew,ItemNum,answer) %>%
  tally()%>%
  mutate(Proportion = n / sum(n),se = sqrt(Proportion*(1-Proportion)/n))%>%
  filter(GroupNew=="control 2")->d.fc.control2

ggplot(data=d.fc.control2,aes(x=answer,y=Proportion))+
  stat_summary(geom = "bar", fun.y = "mean", aes(fill=answer),color="black",position = position_dodge())+
  geom_hline(yintercept = 0.5,colour="blue",linetype = 2)+
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  facet_wrap(~ItemNum,ncol = 5)+
  geom_rect(data = subset(d.fc.control2,ItemNum %in% nonsigitem.fc.c2),
            xmin = -Inf,xmax = Inf,ymin = -Inf,ymax = Inf,
            colour="red",size=1.5,alpha = 0)+
  labs(y="Proportion of Choice",title="Control 2 group: Individual-item")+
  scale_fill_discrete(name="Answer")+
  theme_bw(base_size = 12)+
  theme(legend.position = c(0.95, 0.09))->p.fc.c2.hl

p.fc.c2.hl
```

# R Session Information
```{r}
sessionInfo()
```